---
title: "Exam 2016"
output: html_document
---

The following will be performed for each question: 

a) Tidy the datasets (if required);
b) Generate summary statistics and exploratory figures/tables to characterise the data;
c) Undertake hypothesis testing. In each case, you must clearly state the:
   Hypothesis being tested;
   Type of data being analysed;
   Statistical test(s) chosen to assess the hypothesis/hypotheses;
   The assumptions of the test(s);
d) Core information describing the output of the statistical test(s);
e) Conclusions you can draw from the analysis.
f) Use your analysis to answer the posed question (where appropriate)

The following are packages that could be used for data analysis:

library(readr)
library(ggplot2)
library(favstats)
library(tidyr)
library(tidyverse)
library(readr)
library(mosaic)
library(lattice)
library(datasets)
library(Matrix)
library(mosaicData)
library(dplyr)
library(stats)
library(base)
library(datasets)
library(likert)



Question 1
```{r Question 1a, echo=TRUE}

library(stats)
library(readr)
library(dplyr)
library(tidyr)
library(dplyr)


library(readr)
question1a <- read_csv("C:/Users/LORD DANNICUS/Desktop/stats exam/question1a.csv")
View(question1a)

bt <- question1a
bt
summary(bt)

boxplot(bt)
bt1 <- gather(bt, 'body_temperature', 'value', body_temperature_male:body_temperature_female)

print.data.frame(bt1)

t.test(value~body_temperature, data = bt1, paired = FALSE)

wilcox.test(value~body_temperature, data = bt1, paired = FALSE)
```

```{r question1b, echo=TRUE}

library(readxl)
question1b <- read_excel("C:/Users/LORD DANNICUS/Desktop/stats exam/question1b.xlsx")
View(question1b)

hr <- question1b
hr
summary(hr)
boxplot(hr)

hr1 <- gather(hr, 'heart_rate', 'value', male_HR:female_HR)

t.test(value~heart_rate, data = hr1, paired = FALSE)


```



```{r Question2, echo=TRUE}
library(readr)
library(dplyr)
library(tidyr)

library(readr)
question2a <- read_csv("C:/Users/LORD DANNICUS/Desktop/stats exam/question2a.csv")
View(question2a)

df <- question2a
df

dfa <- table(df$handedness, df$first_stumble)

dfa

barplot(dfa)

chisq.test(dfa)
```


```{r question2b}

library(readxl)
question2b <- read_excel("C:/Users/LORD DANNICUS/Desktop/stats exam/question2b.xlsx")
View(question2b)

ab <-question2b
ab

aba <- gather(ab, 'data','direction', handedness:final_position)

aba

abb <- xtabs(~direction+data, data = aba)
abb


fisher.test(abb)

barplot(abb)



  
```


```{r Question3, echo=TRUE}
library(readr)
library(dplyr)
library(stats)
library(ggplot2)
library(readr)
library(mosaic)
library(lattice)
library(datasets)
library(Matrix)
library(mosaicData)

#a)
question3 <- read_csv("C:/Users/LORD DANNICUS/Desktop/stats exam/question3.csv")

ex <- question3

print(question3)

ex1 <- group_by(ex,time)

print(ex1)

#b)

summary.data.frame(ex1)

coef(lm(calories ~ time, data = ex1))

p <- ggplot(ex1, aes(time, calories))+ geom_point() + labs(title = "Time vs calories consumed") 

p + geom_smooth(method = "lm", se = FALSE)

#c)
    #Hypothesis being tested: There is a relationship between time spent running and caloroes consumed.

   #Type of data being analysed: The type of data being compared here are continuous data.

   #Statistical test(s) chosen to assess the hypothesis/hypotheses: Linear Regression model.

   #The assumptions of the test(s): Looks at the association between 2 variables and the data being compared is continuous and normally distributed.


#d)

ex2 <- cor.test(ex1$time, ex1$calories,
                method = "pearson")

print(ex2)

ex3 <- lm(ex1)

summary(ex3)

qqnorm(ex3$residuals, main = "Normal Q-Q Plot")  
qqline(ex3$residuals, col = "red")


plot( x = ex3$fitted, y = ex3$residuals, main = 'Heteroskedasticy plot')
abline(h = 0, col = 'red')



```



